---
title: "Homework 1"
author: "Jared Klug"
date: "9/15/2020"
output: github_document
---
```{r load_lib}

library(tidyverse)

```

## Problem 1
* Create a data frame comprised of:
  + a random sample of size 10 from a standard Normal distribution
  + a logical vector indicating whether elements of the sample are greater than 0
  + a character vector of length 10
  + a factor vector of length 10, with 3 different factor “levels”
  
```{r create_df}

prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_pos = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h","i","j"),
    fact_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "mid", "high", "high", "high"))
  )

```

Try mean() for each variable in prob1_df:

```{r try_mean}

mean(pull(prob1_df,samp))
mean(pull(prob1_df, samp_pos))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fact_vec))

```

mean() worked for the variables samp (double) and samp_pos (logical). It did not work for the character vector nor factor vector.  

Try as.numeric() for each variable in prob1_df:

```{r try_numeric, results='hide'}

as.numeric(pull(prob1_df, samp_pos))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fact_vec))

```

as.number() worked for the logical vector and surprisingly the factor vector. R is able to change the data types which is why mean() was able to output a number value for the logic vector; mean() first converted the logic vector in numbers then calculated the mean. 

* In a second code chunk:
    + convert the logical vector to numeric, and multiply the random sample by the result
    + convert the logical vector to a factor, and multiply the random sample by the result
    + convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
    
```{r convert_multiply}

as.numeric(pull(prob1_df, samp_pos)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_pos)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_pos))) * pull(prob1_df, samp)

```

## Problem 2 

```{r load_data}

library(palmerpenguins)

data("penguins", package = "palmerpenguins")

```

* Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:
  + the data in this dataset, including names / values of important variables
  + the size of the dataset (using nrow and ncol)
  + the mean flipper length  
  
The data in the penguins dataset includes `r ncol(penguins)` variables:
`r variable.names(penguins)`.  
A total of `r nrow(penguins)` penguins make up the dataset. (the dataset is `r nrow(penguins)` x `r ncol(penguins)`)
There are `r length(levels(pull(penguins, species)))` different species of penguins in this dataset.  
Excluding the missing values, the average body mass of the penguins is `r round(mean(pull(penguins, body_mass_g), na.rm = TRUE), digits = 2)`g.  
The distribution of sex goes as follows: `r count(penguins,sex)[1,]` | `r count(penguins, sex)[2,]` | `r count(penguins, sex)[3,]`  
The data from the penguins was taken between years `r min(pull(penguins, year))` and `r max(pull(penguins, year))`.  
The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)`mm.  

* Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

```{r load_ggplot}

library (ggplot2)

```

```{r make_scatter}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = factor(species))) + 
  geom_point() + 
  theme_minimal() +
  labs(color = "Species")

ggsave(filename = "penguins.png")
```


