---
title: "Homework 1"
author: "Jared Klug"
date: "9/15/2020"
output: github_document
---
```{r load_lib}
library(tidyverse)
```

## Problem 1
* Create a data frame comprised of:
  + a random sample of size 10 from a standard Normal distribution
  + a logical vector indicating whether elements of the sample are greater than 0
  + a character vector of length 10
  + a factor vector of length 10, with 3 different factor “levels”
  
```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_pos = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h","i","j"),
    fact_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "mid", "high", "high", "high"))
  )

```

Try mean() for each variable in prob1_df:

```{r try_mean}

mean(pull(prob1_df,samp))
mean(pull(prob1_df, samp_pos))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fact_vec))

```

mean() worked for the variables samp (double) and samp_pos (logical). It did not work for the character vector nor factor vector.  

Try as.numeric() for each variable in prob1_df:

```{r try_numeric, results='hide'}

as.numeric(pull(prob1_df, samp_pos))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fact_vec))

```

as.number() worked for the logical vector and surprisingly the factor vector. R is able to change the data types which is why mean() was able to output a number value for the logic vector; mean() first converted the logic vector in numbers then calculated the mean. 

## Problem 2 